О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Updating TODO notes
Iteration: typos and cosmetics

\begin{problem}[Point Packing in a Square (PPS)\cite{locatelli2002packing,costa2013valid}]
	\label{problem:PPS}
	Given an integer $k > 1$, place $k$ points in the unit square $U = [ 0 , 1 ]^2$ such that their
	minimum pairwise distance $m$ is maximal.
\end{problem}

@@

Performing some trivial manipulations with the upper bound in Theorem~\ref{thm:varphi_k_bounds},
one can make the following
\begin{observation}
	\label{varphi_n_where_n_geq_21492}
	For $n \geq 21492$ we have
	\begin{equation}
		\varphi_n \leq \varphi_{n-1} \leq \frac{\beta}{\sqrt{n-2}}
		,
	\end{equation}
	where
	\begin{equation}
		\beta = \frac{1}{\sqrt{21490}} + \sqrt{ \frac{2}{\sqrt{3}} + \frac{1}{21490} } < 1.07464
		.
	\end{equation}
\end{observation}

@@

\begin{proof}
	$n^2+1$ points, including the ends of $\Delta$, split the segment $\Delta$ into $n^2$
	sequential segments $\Delta_i$.
	Due to Lemma~\ref{lem:2k-1_segments}, there is at most one segment of length 1,
	at most three segments of length 2 etc.
	The following two values of sums conclude the proof:
	\begin{equation}
		1 + \sum_{k=1}^n (2k-1) = n^2 + 1
		,
	\end{equation}
	\begin{equation}
		\sum_{k=1}^n k(2k-1) = \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n
		.
	\end{equation}
\end{proof}

@@

\begin{proof}
	For $4 \leq n \leq 21491$, the claim of the theorem follows immediately from Observation~\ref{obs:4_leq_n_leq_21491}.
	Let us consider $M\in \mathfrak{M}(2,n)$, $n \geq 21492$, $\operatorname{diam} M = b$.
	Lemma~\ref{lem:square_container} yields that $M$ is situated is a square with side length $b$.
	Let $M_1, M_2, M_3, M_4$ be points of $M$ such that the distances $|M_1-M_2|$ and $|M_3-M_4|$
	are minimal in $M$ ($M_2$ and $M_3$ may be the same point).
	Then $|M_1-M_2| \leq b\varphi_{n-1}$ and $|M_3-M_4| \leq b\varphi_{n-1}$.
	Due to Lemma~\ref{lemma:quadr_diag_edges}, open line segments $M_1 M_2$ and $M_3 M_4$ do not intersect
	(otherwise they are not minimal).

	Let $C = cr(M_1 M_2) \cap cr(M_3 M_4)$.
	Each point of $n\in M$ satisfies one of the following conditions:

@@

For every integer $n\geq 3$ Solymosi~\cite{solymosi2003note} gives a construction of a facher integral point set
$M\in\mathfrak{M}(2,n)$
such that equality $|M_1 - M_2| = 2$ holds for some $M_1, M_2 \in M$.
The constructed set has both odd and even distances.

@@

	Note that all the points $M_{J\pm}$ are distinct:
	the equality $b_J = b_K$ implies $J=K$;
	the equality $b_J = b_K$ implies $c_J = -c_K$ or $c_J = a / c_k$.
	The first case is impossible because both $c_J$ and $c_K$ are positive;
	the second case contradicts with~\eqref{eq:a_equiv_3_mod_4} and~\eqref{eq:c_J_equiv_1_mod_4}.

	So, $M = \{ M_{J\pm}, N\}$ is indeed a planar integral point set of $2^k+1$ points,
	and distance 1 occurs in $M$.
	Reminding that $k$ can be taken arbitrary large, we conclude that we can construct
	a planar integral point set of arbitary large count of points so that the distance 1 occurs in that set.
\end{construction}

TODO: recalculate the cardinality.

@@

TODO: should I write translated version of the results here?

>>>>

\begin{problem}[Point Packing in a Square (PPS)~\cite{locatelli2002packing,costa2013valid}]
	\label{problem:PPS}
	Given an integer $k > 1$, place $k$ points in the unit square $U = [ 0 , 1 ]^2$ such that their
	minimum pairwise distance $m$ is maximal.
\end{problem}

@@

Performing some simple manipulations with the upper bound in Theorem~\ref{thm:varphi_k_bounds},
one can make the following
\begin{observation}
	\label{varphi_n_where_n_geq_21492}
	For $n \geq 21492$ we have
	\begin{equation}
		\varphi_n \leq \varphi_{n-1} \leq \frac{\beta}{\sqrt{n-2}}
		,
	\end{equation}
	where
	\begin{equation}
		\beta = \frac{1}{\sqrt{21490}} + \sqrt{ \frac{2}{\sqrt{3}} + \frac{1}{21490} } < 1.07464
		.
	\end{equation}
\end{observation}

@@

\begin{proof}
	$n^2+1$ points, including the ends of $\Delta$, split the segment $\Delta$ into $n^2$
	sequential segments $\Delta_i$.
	Due to Lemma~\ref{lem:2k-1_segments}, there is at most one segment of length 1,
	at most three segments of length 2, etc.
	The following two values of sums conclude the proof:
	\begin{equation}
		1 + \sum_{k=1}^n (2k-1) = n^2 + 1
		,
	\end{equation}
	\begin{equation}
		\sum_{k=1}^n k(2k-1) = \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n
		.
	\end{equation}
\end{proof}

@@

\begin{proof}
	For $4 \leq n \leq 21491$, the claim of the theorem follows immediately from Observation~\ref{obs:4_leq_n_leq_21491}.
	Let us consider $M\in \mathfrak{M}(2,n)$, $n \geq 21492$, $\operatorname{diam} M = b$.
	Lemma~\ref{lem:square_container} yields that $M$ is situated in a square with side length $b$.
	Let $M_1, M_2, M_3, M_4$ be points of $M$ such that the distances $|M_1-M_2|$ and $|M_3-M_4|$
	are minimal in $M$ ($M_2$ and $M_3$ may be the same point).
	Then $|M_1-M_2| \leq b\varphi_{n-1}$ and $|M_3-M_4| \leq b\varphi_{n-1}$.
	Due to Lemma~\ref{lemma:quadr_diag_edges}, open line segments $M_1 M_2$ and $M_3 M_4$ do not intersect
	(otherwise they are not minimal).

	Let $C = cr(M_1 M_2) \cap cr(M_3 M_4)$.
	Each point of $N\in M$ satisfies one of the following conditions:

@@

For every integer $n\geq 3$ Solymosi presented~\cite{solymosi2003note} a construction of a facher integral point set
$M\in\mathfrak{M}(2,n)$
such that equality $|M_1 - M_2| = 2$ holds for some $M_1, M_2 \in M$.
The constructed set has both odd and even distances.

@@

	Note that all the points $M_{J\pm}$ are distinct:
	the equality $b_J =  b_K$ implies $J=K$;
	the equality $b_J = -b_K$ implies $c_J = -c_K$ or $c_J = a / c_K$.
	The first case is impossible because both $c_J$ and $c_K$ are positive;
	the second case contradicts with~\eqref{eq:a_equiv_3_mod_4} and~\eqref{eq:c_J_equiv_1_mod_4}.

	So, $M = \{ M_{J\pm}, N\}$ is indeed a planar integral point set of $2^k+1$ points,
	and distance 1 occurs in $M$.
	Reminding that $k$ can be taken arbitrary large, we conclude that we can construct
	a planar integral point set of arbitrary large count of points so that the distance 1 occurs in that set.
\end{construction}

@@

TODO: write the translated version of the results here
